Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-05-24 edubots_surveys.Rnw
adds script for population description and some text refs #13
Revising the Introduction

\begin{abstract} % abstract
Introducing new technologies such as messaging platforms, and chatbots attached to it, in higher education, requires careful consideration of all options, but above all, an examination of the attitudes of the affected community. In this paper we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish speaking countries, looking at what they think of the introduction of messaging platforms and chatbots, what their needs are, what kind of use cases they see for them, and in what kind of environment they think its use will be valuable. We will examine how and when these attitudes vary across gender, experience, and other factors, such as the kind of discipline they are teaching. Our conclusions might help with the adoption of messaging platforms, as well as chatbots or other kind of bots, by higher education institution, and how these must be introduced to teachers so that it helps them achieve desired educational outcomes.
\end{abstract}

@@

% TODO: introduction
The introduction of new technologies in the classroom needs a combination of teacher education, student willingness and (possibly new) skills in both. Some technologies are readily adapted, some of them take a long time to be adopted. In most cases, success or failure of the introduction of a new technology impinges on the colaboration of all the implied parties, which is why evaluating attitudes towards them is an essential first step.

In the framework of the Edubots KA2 European projects, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms. A \textit{chatbot} is a program that allows a computer to communicate in a similar way as a human does \cite{Gong2008}, using natural language. Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker’s question fluently, and even ask other questions to the human.

The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with. These automatic systems ease personalized learning, adapting individuals' pace of learning, who get personalized online tutoring outside the classroom. Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.

In this sense, chatbot technology offers a great opportunity for the improvement of tutoring systems \cite{Daniel2016,agarwal2020}, as not all students are comfortable with face-to-face tutoring with the instructor. In fact, in many cases, students suffer from stress when they have to ask a question in front of the entire class. This is why many students prefer to remain silent and ask their question later via email. 
However, this means a waste of time and a delay of hours or even days to get the teacher's answer.
Chatbot technology has a potential to fill the gap between teacher and students, helping them to solve questions and carry out a dynamic and autonomous learning \cite{Griol2014,kim2020}.
Moreover, using an automated system such as a chatbot allows the teacher to detect those topics that are most in demand, and on which he or she should consequently place more emphasis in class.

Chatbots are obviously associated to messaging applications, and in particular, direct messaging applications, since they are the only time of applications that are able to support a synchronous conversation betweeh the two parties. This is why in many cases chatbots couple messaging and the chatbot technology itself \cite{differ.chat}, while in others, you can create chatbots in any number of technologies and then attach them to a messaging application using their API.

% Maybe move it to a different place later
As a starting point, we have analyzed the responses to a survey from 300 teachers asking about their attitudes towards the use of chatbots in their classes. We are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
\begin{itemize}
\item{ RQ1 - Are teachers already using messaging apps in their classes? } %This was the second survey, not the  first survey. I wonder if maybe we could invert the presentation order - JJ
\item{ RQ2 -  Which kind of chatbots would teachers find useful in their classes?? }

@@

@@

@@

@@

>>>>

\begin{abstract} % abstract
Introducing new technologies such as messaging platforms, and chatbots attached to it, in higher education, requires careful consideration of all options, but above all, an examination of the attitudes of the affected community. 
% Antonio - En realidad, la comunidad afectada incluiría también a los estudiates, ¿no?
% Por cierto, quizá también se podrían incluir aqui las encuestas pasadas a los estudiantes. No son las mismas preguntas, pero van en una línea similar. Quizá tuviesen cabida y le darían 
% más enjundia al estudio. ;)
In this paper we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish speaking countries, looking at what they think about the introduction of messaging platforms and chatbots, what their needs are, what kind of use cases they see for them, and in what kind of environment they think its use will be valuable. We will examine how and when these attitudes vary across gender, experience, and other factors, such as the kind of discipline they are teaching. Our conclusions might help with the adoption of messaging platforms, as well as chatbots or other kind of bots, by higher education institution, and how these must be introduced to teachers so that it helps them achieve desired educational outcomes.
\end{abstract}

@@

% TODO: introduction
The introduction of new technologies in the classroom needs a combination of teacher education, student willingness and (possibly new) skills in both. Some technologies are readily adapted, but some of them take a long time to be adopted. In most cases, the success or failure of the introduction of a new technology impinges on the colaboration of all the implied parties, which is why evaluating attitudes towards them is an essential first step.

In the framework of the Edubots KA2 European project, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms. A \textit{chatbot} is a program, based on Artificial Intelligence techniques, that allows a computer to communicate in a similar way as a human does \cite{Gong2008}, using natural language. Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker’s question fluently, and even ask other questions to the human.

The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with. These automatic systems ease personalized learning, 
% customized en lugar de personalized? Por no repetir personalized dos veces en la misma frase
adapting individuals' pace of learning, who get personalized online tutoring outside the classroom. Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.

In this sense, chatbot technology offers a great opportunity for the improvement of tutoring systems \cite{Daniel2016,agarwal2020}, as not all students are comfortable with face-to-face tutoring with the instructor. In fact, in many cases, students suffer from stress when they have to ask a question in front of the entire class. This is why many students prefer to remain silent and ask their question later via email. 
However, this means a waste of time and a delay of hours or even days to get the teacher's answer.
Chatbot technology has a potential to fill the gap between teacher and students, helping them to solve questions and carry out a dynamic and autonomous learning \cite{Griol2014,kim2020}.
Moreover, using an automated system such as a chatbot allows the teacher to detect the most demanded topics, and on which he or she should consequently place more emphasis in class.

Chatbots are obviously associated to messaging applications, and in particular, direct messaging applications, since they are the only type of applications that are able to support a synchronous conversation between the two parties. This is why in many cases chatbots couple messaging and the chatbot technology itself \cite{differ.chat}, while in others, you can create chatbots in any number of technologies and then attach them to a messaging application using their API (Application Program Interface).

% Maybe move it to a different place later
Given the potential advantages that chatbots could bring to the classroom, as a previous step, we have performed a survey to 300 teachers asking about their attitudes towards the use of chatbots in their classes. We analyse in this work their responses, since we are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
\begin{itemize}
\item{ RQ1 - Are teachers already using messaging apps in their classes? } %This was the second survey, not the  first survey. I wonder if maybe we could invert the presentation order - JJ
\item{ RQ2 -  Which kind of chatbots would teachers find useful in their classes?? }

@@

% ********************** STATE OF THE ART ****************************

@@

% ********************** RESULTS ****************************

@@

\begin{figure}[t]
\begin{center}
    \begin{minipage}[t]{0.3\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.3\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/age.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.3\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector.pdf}
    \end{minipage}

    \vspace{0.5mm}
    \begin{minipage}[t]{0.3\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.55\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/discipline.pdf}
    \end{minipage}
\end{center}
    \caption{Sample population description. A total 282 teachers shown by gender, age, sector (university and vocational education), number of years of experience in education, and discipline.}
\label{figure:teachers_population}
\end{figure}

@@

% ********************** CONCLUSIONS ****************************
